Global patterns of forest autotrophic carbon fluxes

### 2021-02-23 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

```{r setup, include = FALSE}
#knitr::opts_knit$set(root.dir = 'C:/Users/becky/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
  # knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = '/Users/gyrcbm/Documents/GitHub/Global_Productivity/manuscript/')
```

>>>>

```{r setup, include = FALSE}
#knitr::opts_knit$set(root.dir = 'C:/Users/becky/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
  # knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
# knitr::opts_knit$set(root.dir = '/Users/gyrcbm/Documents/GitHub/Global_Productivity/manuscript/')
```
